Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-29 paper/ms.tex
Even more on Carlyn's paper.

Assuming a hybrid WD forms, there is subsequent evolution that will occur.

\citep{schwabgaraud2018}

Hybrid models 
old 
\citep{denissenkovetal2015}
\citet{Wangetal2014} and \citet{Mengetal2014} presented binary

see however~\cite{lecoanetetal16}

Recent results from stellar evolution
The models we are exploding \citep{brooksetal2017}

@@

Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
Give a read to see! Reading says no, but confirm.

Also, recent population synthesis work indicating a substantial contribution
to the Ia population rate from mergers where one member is a 
hybrid~\citep{yungelsonkuranov2017}.

>>>>

Assuming a hybrid WD forms, there is subsequent evolution that will occur. There
are two ways in which a hybrid WD can become a progenitor of a thermonuclear supernova.
First, the hybrid could be part of a binary system in which the companion star becomes
another white dwarf and the two merge. Recent population synthesis work supports
this pathway by indicating a substantial contribution to the Ia population rate from 
mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. The second way
occurs if the hybrid WD is part of a binary with a main sequence or giant companion
and gains enough mass to approach the Chandrasekhar mass and ignite C fusion (i.e.
the single degenerate picture)~\citep{}.

In either case, the hybrid WD will experience a period of cooling, which will
make the core-mantle interface subject to convective 
instability \citep{brooksetal2017,schwabgaraud2018}. In the case of the 
hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
heat the core and start C fusion, leading to a period of ``simmering" prior
to the explosion \citep{who?}. The upshot is that is likely to be considerable
mixing after the hybrid forms that may homegenize the compostion 
\citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.

Hybrid WDs have more mass than traditional C/O WDs, with some studies indicating the
mass can approach 1.3 \Msun \citep{chenetal2014}. This increased mass
minimizes one of the problems associated with the single-degenerate picture,
the need to accrete enough mass for the WD to approach the Chandrasekhar
mass~\citep{chenetal2014,denissenkovetal2015,kromeretal2015}.
Accordingly, there has been considerable interest in viability of explosions from 
these progenitors.

From population synthesis, \citet{mengpods2014} found that these
%meng received may 5 accepted may 16
progenitors may substantially contribue to the population of SNeIa (1-8\%) and have
relatively short delay times. They also suggested that these 
may produce part of the Iax class of events. \citet{Wangetal2014} also with population
synthesis studied the case
%received august 28 accepted sept 26
of a hybrid progenitor accreting from a nondegenerate He star and found
birth rates indicating that up to 18\% of SNe Ia may follow from this chanel
and very short delay times. \citet{Wangetal2014} also suggested that explosions 
from hybrid progenitors may provide an explanation for type Iax events.
\citet{mengpods2018}, from the common-envelope-wind model developed in 
\citep{mengpods2014}, propose that both Ia-CSM and Iax events 
are caused by the explosion of hybrid progenitors, with Ia-CSM occuring in systems with 
a massive common envelope and Iax events occuring in systems where most of the common envelope
has been lost.

Other groups have simulated explosions from hybrid progenitors. 
\citet{kromeretal2015} performed pure deflagration simulations from models 
with a C core. They found that their models may explain some faint events 
such as SN 2008ha~\citep{foleyetal2009}.
\citet{bravoetal2016} performed one-dimensional simulations of explosions from 
a variety of progenitor models assuming both pure deflagration and the DDT 
explosion mechanism. 
Some of their models are similar to those of \citep{denissenkovetal2015} and 
they report that many models produce less synthesized
\Ni{56}, indicating dimmer events. They also note that some of their
models may explain Iax events.

\citet{willcoxetal2016} simulated explosions from the progenitors of 
\citep{denissenkovetal2015} and

@@
